3D seismic diffraction separation and imaging using the local rank-reduction method

### 2022-01-07 diffrlrra3d/paper.tex
up

%% uncomment
%\multiplot{4}{b,b-pwd,b-lrr,b-lrra}{width=0.45\columnwidth}{Field data example. (a) A 3D field dataset. Separated reflection data using (b) the PWD method, (c) the LRR method, and (d) the LRRA method. }
%\multiplot{3}{b-pwd-n-0,b-lrr-n-0,b-lrra-n-0}{width=0.45\columnwidth}{Separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }

%\multiplot{3}{b-pwd-n-t-0,b-lrr-n-t-0,b-lrra-n-t-0}{width=0.45\columnwidth}{A comparison of time slices extracted from the separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }

%\multiplot{4}{b-pwd-rimag-0,b-pwd-imag-0,b-lrr-imag-0,b-lrra-imag-0}{width=0.45\columnwidth}{(a) Time slice of the reflection image. Time slices of the diffraction image using (b) the PWD method, (c) the LRR method, and (d) the LRRA method. The arrows indicate the higher resolution using the LRRA method and the lower resolution of the PWD method due to the consistency in depicting the crossline-oriented paleo-channel between the reflection and diffraction images.}
%

>>>>

%% uncomment
\inputdir{real3d}
\multiplot{4}{b,b-pwd,b-lrr,b-lrra}{width=0.45\columnwidth}{Field data example. (a) A 3D field dataset. Separated reflection data using (b) the PWD method, (c) the LRR method, and (d) the LRRA method. }
\multiplot{3}{b-pwd-n-0,b-lrr-n-0,b-lrra-n-0}{width=0.45\columnwidth}{Separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }

\multiplot{3}{b-pwd-n-t-0,b-lrr-n-t-0,b-lrra-n-t-0}{width=0.45\columnwidth}{A comparison of time slices extracted from the separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }

\multiplot{4}{b-pwd-rimag-0,b-pwd-imag-0,b-lrr-imag-0,b-lrra-imag-0}{width=0.45\columnwidth}{(a) Time slice of the reflection image. Time slices of the diffraction image using (b) the PWD method, (c) the LRR method, and (d) the LRRA method. The arrows indicate the higher resolution using the LRRA method and the lower resolution of the PWD method due to the consistency in depicting the crossline-oriented paleo-channel between the reflection and diffraction images.}
%
